---
title: "Results_different_variance_D"
author: "Dongni Zhang"
date: '2024-01-08'
output: html_document
---

```{r include=FALSE}
# include packages
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#library(tidyverse)
library(metR)
#install.packages('metR')
library(ggplot2)
#install.packages("pracma")
library(pracma)#AUC
library(rootSolve)
#install.packages("sparsevar")
library(sparsevar)
library(cowplot)
require(gridExtra)
```

# Basic reproduction number: without CT
```{r}
R_0 = function(mu, sigma, beta_N, beta_G, tau){
  
## assume D has mean mu and variance sigma^2

# For type-2 (infected through global contacts), the expected size-biased degree minus 1 would be
mean_mean_D_tilde_minus_1 = mu + (sigma^2-mu)/mu

############################################  
# elements of the next generation matrix
############################################
mNN = mean_mean_D_tilde_minus_1*(1-exp(-beta_N*tau))
mHN = mu*(1-exp(-beta_N*tau))
mHH = beta_G*tau
mNH = beta_G*tau

M <- matrix(c(mNN, mNH, mHN, mHH), 2, 2, byrow=TRUE)
  
#ev <- eigen(M)

#eigenvalues <- ev$values

return(spectralRadius(M))

}
```

# Manual Reproduction Number
```{r}
######################################################
# Manual with delay on network 
######################################################
# type-1 (N,R): infected through network (N) and reported (R)\\
# type-2 (N,NR): infected through network and not reported (NR)\\
# type-3 (H): infected through homogeneous contacts (H)
######################################################
######################################################

# assume T_L, T_D deterministic

R_manual_delay = function(mu, sigma, beta_N, beta_G, tau, p_D, T_L, T_D, p_M){
  
mean_mean_D_tilde_minus_1 = mu + (sigma^2-mu)/mu

############################################  
# elements of the next generation matrix M: 
############################################
  
# For type-1: 

m12 = mean_mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_D*p_M
m11 = mean_mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-p_D*p_M)
m13 = beta_G*tau

# For type-3: 
m32 = mu*(1-exp(-beta_N*tau))*p_D*p_M
m31 = mu*(1-exp(-beta_N*tau))*(1-p_D*p_M)
m33 = beta_G*tau

# For type-2: 
# let 
T_DL = T_D-T_L

# probability: P(recovered before being traced)
if (tau <= T_DL){
  p_r = 1
}
if (T_DL <= 0){
  p_r = 0
}
if (T_DL < tau && 0 < T_DL){
  p_r = (T_D-T_L)/tau
}

# probability: P(infecting a given friend, given that traced before recovered)

if (tau <= T_DL){
  p_i_c = 0
}
if (T_DL <= -tau){
  p_i_c = 0
}
if (T_DL < 0 && T_DL > -tau){
  p_i_c = (tau+T_DL)/tau - (1- exp(-beta_N * (tau+T_DL)))/(beta_N * tau)
}
if (T_DL < tau && T_DL >= 0){
  p_i_c = (tau-T_DL)/tau - (exp(-beta_N * T_DL)- exp(-beta_N * tau))/(beta_N * tau)
}

#print(p_i_c)

# if being traced, the expected infectious period (shortened by CT)

if (tau <= T_DL){
  V = 0
}
if (T_DL <= -tau){
  V = 0
}
if (T_DL < 0 && T_DL > -tau){
  V = (tau-T_L+T_D)^2 /(2*tau)
}
if (T_DL < tau && T_DL >= 0){
  V = (tau+T_L-T_D)*(tau-T_L+T_D)/(2*tau)
}

#print(V)

m21 = mean_mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_r*(1-p_M*p_D) + mean_mean_D_tilde_minus_1*p_i_c
m22 = mean_mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_r*p_D*p_M
m23 = beta_G * V  + beta_G*tau*p_r
    
M_manual <- matrix(c(m11, m12, m13, m21, m22, m23, m31,m32, m33), 3, 3, byrow=TRUE)
  
#ev <- eigen(M)

#eigenvalues <- ev$values

return(spectralRadius(M_manual))
  
}
```

# Digital reproduction number
```{r}
######################################################
# Digital CT
######################################################
# pi: fraction of app-users
######################################################
######################################################

# assume T_L, T_D constant

R_digital_network = function(mu, sigma, beta_N, beta_G, tau, p_D, T_L, pi){
  
mean_D_tilde_minus_1 = mu + (sigma^2-mu)/mu

# elements of the next generation matrix M: 

######################################################
# Type-1: non-app-user infected without DCT-link, through network. 
# Type-2: non-app-user infected without DCT-link, through homo. 
# Type-3: app-user infected without DCT-link, through network. 
# Type-4: app-user infected without DCT-link, through homo. 

# Type-5: app-user infected with DCT-link, through network. 
# Type-6: app-user infected with DCT-link, through homo. 
######################################################

m11 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-pi)
m12 = beta_G * tau * (1-pi)
m13 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(pi)
m14 = beta_G * tau * (pi)
m15 = 0
m16 = 0

m21 = mu*(1-exp(-beta_N*tau))*(1-pi)
m22 = beta_G * tau * (1-pi)
m23 = mu*(1-exp(-beta_N*tau))*(pi)
m24 = beta_G * tau * (pi)
m25 = 0
m26 = 0

m31 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-pi)
m32 = beta_G * tau * (1-pi)
m33 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-p_D)*(pi)
m34 = beta_G * tau *(1-p_D) *(pi)
m35 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(p_D)*(pi)
m36 = beta_G * tau *(p_D) *(pi)


m41 = mu*(1-exp(-beta_N*tau))*(1-pi)
m42 = beta_G * tau * (1-pi)
m43 = mu*(1-exp(-beta_N*tau))*(1-p_D)*(pi)
m44 = beta_G * tau *(1-p_D) *(pi)
m45 = mu*(1-exp(-beta_N*tau))*(p_D)*(pi)
m46 = beta_G * tau *(p_D) *(pi)



# probability that a to-be-traced app-user infects a given friend: '
# Note: in this case, the app-user is always traced first before recovered itself

if (T_L < tau){
  p_inf = (tau-T_L)/tau - (1- exp(-beta_N * (tau-T_L)))/(beta_N * tau)
}
if (T_L >= tau){
  p_inf = 0
}

# the average time since being infectious until traced: 

if (T_L < tau){
  T_inf = (tau-T_L)^2 /(2*tau)
}
if (T_L >= tau){
  T_inf = 0
}
 
  
m51 = mean_D_tilde_minus_1*p_inf*(1-pi)
m52 = beta_G * T_inf * (1-pi)
m53 = mean_D_tilde_minus_1*p_inf*(pi)
m54 = beta_G * T_inf *(pi)
m55 = 0
m56 = 0

m61 = mu*p_inf*(1-pi)
m62 = beta_G * T_inf * (1-pi)
m63 = mu*p_inf*(pi)
m64 = beta_G * T_inf *(pi)
m65 = 0
m66 = 0


M_digital <- matrix(c(m11, m12, m13, m14, m15, m16, 
                      m21, m22, m23, m24, m25, m26,
                      m31,m32, m33, m34,m35,m36, 
                      m41,m42,m43,m44,m45,m46,
                      m51,m52,m53,m54,m55,m56,
                      m61,m62,m63,m64,m65,m66), 6, 6, byrow=TRUE)
  
#ev <- eigen(M_digital)

#eigenvalues <- ev$values

# Compute the spectral radius of M: the maximum of the absolute values of its eigenvalues
return(spectralRadius(M_digital))
  
}
```

# Combined reproduction number: 
```{r}
######################################################
# Combined CT (manual on network; digital on both)
######################################################
# assume T_L, T_D constant
# assume D has mean mu and variance sigma^2

R_comb = function(mu, sigma, beta_N, beta_G, tau, p_D, T_L, T_D, p_M, pi){

######################################################
# Type-1: non-app-user infected without DCT-link, without MCT-link, through network. 
# Type-2: non-app-user infected without DCT-link, with MCT-link, through network.
# Type-3: non-app-user infected without DCT-link, without MCT-link, through homo. 
  
# Type-4: app-user infected without DCT-link, without MCT-link, through network. 
# Type-5: app-user infected without DCT-link, with MCT-link, through network. 
# Type-6: app-user infected with DCT-link,-----, through network. 
# Type-7: app-user infected without DCT-link, without MCT-link, through homo. 
# Type-8: app-user infected with DCT-link, without MCT-link, through homo. 
######################################################
  
mean_D_tilde_minus_1 = mu + (sigma^2-mu)/mu

m_11 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-p_D*p_M)*(1-pi)
m_12 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(p_D*p_M)*(1-pi)  
m_13 = beta_G * tau* (1-pi)
m_14 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-p_D*p_M)*(pi)
m_15 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(p_D*p_M)*(pi)
m_16 = 0
m_17 = beta_G * tau* (pi)
m_18 = 0 


if (tau+T_L-T_D <= 0){
  p_r = 1
}
if (tau+T_L-T_D >= tau){
  p_r = 0
}
if (0<tau+T_L-T_D && tau+T_L-T_D < tau){
  p_r = (T_D-T_L)/tau
}

# probability: P(infecting a given friend, traced before recovered)
T_DL = T_D-T_L

if (T_DL < tau && T_DL >= 0){
  p_i_c = (tau-T_DL)/tau - (exp(-beta_N * T_DL)- exp(-beta_N * tau))/(beta_N * tau)
}
if (T_DL < 0 && T_DL > -tau){
  p_i_c = (tau+T_DL)/tau - (1- exp(-beta_N * (tau+T_DL)))/(beta_N * tau)
}
if (T_DL >= tau){
  p_i_c = 0
}
if (T_DL <= -tau){
  p_i_c = 0
}

if (T_DL < tau && T_DL >= 0){
  V = (tau+T_L-T_D)*(tau-T_L+T_D)/(2*tau)
}
if (T_DL < 0 && T_DL > -tau){
  V = (tau-T_L+T_D)^2 /(2*tau)
}
if (T_DL >= tau){
  V = 0
}
if (T_DL <= -tau){
  V = 0
}


m_21 = (mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_r*(1-p_M*p_D) + mean_D_tilde_minus_1*p_i_c)*(1-pi)
m_22 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_D*p_M*p_r*(1-pi)
m_23 = (beta_G * V  + beta_G*tau*p_r)*(1-pi)
m_24 = (mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_r*(1-p_M*p_D) + mean_D_tilde_minus_1*p_i_c)*(pi)
m_25 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_D*p_M*p_r*pi
m_26 = 0 
m_27 = (beta_G * V  + beta_G*tau*p_r)*(pi)
m_28 = 0 


m_31 = mu*(1-exp(-beta_N*tau))*(1-p_D*p_M)*(1-pi)
m_32 = mu*(1-exp(-beta_N*tau))*(p_D*p_M)*(1-pi)
m_33 = beta_G*tau*(1-pi)
m_34 = mu*(1-exp(-beta_N*tau))*(1-p_D*p_M)*(pi)
m_35 = mu*(1-exp(-beta_N*tau))*(p_D*p_M)*(pi)
m_36 = 0
m_37 = beta_G*tau*(pi)
m_38 = 0 


m_41 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-p_D*p_M)*(1-pi)
m_42 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(p_D*p_M)*(1-pi)
m_43 = beta_G * tau* (1-pi)
m_44 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(1-p_D)*(pi)
m_45 = 0
m_46 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*(p_D)*(pi)
m_47 = beta_G * tau*(1-p_D)*(pi)
m_48 = beta_G * tau*(p_D)*(pi)

m_51 = m_21
m_52 = m_22
m_53 = m_23
m_54 = (mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_r*(1-p_D) + mean_D_tilde_minus_1*p_i_c)*(pi)
m_55 = 0 
m_56 = mean_D_tilde_minus_1*(1-exp(-beta_N*tau))*p_r*(p_D)*pi
m_57 = (beta_G * V  + beta_G*tau*p_r*(1-p_D))*(pi)
m_58 = beta_G*tau*p_r*(p_D)*(pi)


if (T_L < tau){
  p_inf = (tau-T_L)/tau - (1- exp(-beta_N * (tau-T_L)))/(beta_N * tau)
}
if (T_L >= tau){
  p_inf = 0
}

# the average time since being infectious until traced: 

if (T_L < tau){
  T_inf = (tau-T_L)^2 /(2*tau)
}
if (T_L >= tau){
  T_inf = 0
}


m_61 = mean_D_tilde_minus_1*p_inf*(1-pi)
m_62 = 0
m_63 = beta_G * T_inf * (1-pi)
m_64 = mean_D_tilde_minus_1*p_inf*(pi)
m_65 = 0
m_66 = 0 
m_67 = beta_G * T_inf * (pi)
m_68 = 0
  
m_71 = mu*(1-exp(-beta_N*tau))*(1-p_D*p_M)*(1-pi)
m_72 = mu*(1-exp(-beta_N*tau))*(p_D*p_M)*(1-pi)
m_73 = beta_G*tau*(1-pi)
m_74 = mu*(1-exp(-beta_N*tau))*(1-p_D)*pi
m_75 = 0
m_76 = mu*(1-exp(-beta_N*tau))*(p_D)*pi
m_77 = beta_G*tau*(1-p_D)*(pi)
m_78 = beta_G*tau*(p_D)*(pi)

m_81 = mu*p_inf*(1-pi)
m_82 = 0
m_83 = beta_G * T_inf * (1-pi)
m_84 = mu*p_inf*(pi)
m_85 = 0
m_86 = 0 
m_87 =  beta_G * T_inf * (pi)
m_88 = 0



M_combine <- matrix(c(m_11, m_12, m_13, m_14, m_15, m_16, m_17,m_18, 
                      m_21, m_22, m_23, m_24, m_25, m_26,m_27,m_28,
                      m_31, m_32, m_33, m_34, m_35, m_36,m_37,m_38,
                      m_41, m_42, m_43, m_44, m_45, m_46,m_47,m_48,
                      m_51, m_52, m_53, m_54, m_55, m_56,m_57,m_58,
                      m_61, m_62, m_63, m_64, m_65, m_66,m_67,m_68,
                      m_71, m_72, m_73, m_74, m_75, m_76,m_77,m_78,
                      m_81, m_82, m_83, m_84, m_85, m_86,m_87,m_88), 8, 8, byrow=TRUE)
  
#ev <- eigen(M_combine)

#eigenvalues <- ev$values

# Compute the spectral radius of M: the maximum of the absolute values of its eigenvalues
return(spectralRadius(M_combine))
  
}
```

# Set epidemic parameters 
```{r} 
# infectious period (deterministic)
tau=5
# latency period (deterministic)
T_L=4
# mean degree 
mu = 5
# standard deviation of D
sigma = 10

# we choose beta_G beta_N so that R0 =3
# assume that beta_G = mu*beta_N "equal weights"

f1 <- function(x){R_0(mu=mu, sigma=sigma, 
                    beta_G = mu*x, beta_N = x, 
                    tau=tau)-3}
beta_N = uniroot(f1,c(0,1))$root
beta_G = mu*beta_N


#other option: we choose beta_G beta_N so that small R0 =1.5

f2 <- function(x){R_0(mu=mu, sigma=sigma, 
                    beta_G = mu*x, beta_N = x, 
                    tau=tau)-1.5}
beta_N_s = uniroot(f2,c(0,1))$root
beta_G_s = mu*beta_N_s



```

# Heatmap of R_M (fix T_D, vary p_M and p_D)

```{r}
n_grid=100

# Fix delay to be 3 days
T_D = 3
#T_D = 1

# p_M takes values in 
p_seq = seq(0,1, length.out=n_grid)

# p_D takes values in 
p_D_seq = seq(0.01,1, length.out=n_grid)

# store the R_M values in a matrix:
R_M_m=matrix(nrow = n_grid,ncol = n_grid)

# store the R_M values in a matrix (for small R0)
R_M_s_m=matrix(nrow = n_grid,ncol = n_grid)


for (k in (1:n_grid)) {
  
  p1 = p_seq[k]
  
  for (j in (1:n_grid)) {
    
  p2 = p_D_seq[j] 
  
  R = R_manual_delay(mu=mu, sigma=sigma, 
                     beta_N= beta_N, beta_G= beta_G, 
                     tau=tau, T_L= T_L, T_D=T_D,
                     p_M=p1,p_D=p2)
  
  
  R_M_m[j,k] = R
  
  Rs = R_manual_delay(mu=mu,sigma=sigma, 
                      beta_N= beta_N_s, beta_G= beta_G_s, 
                     tau=tau, T_L= T_L, T_D=T_D,
                     p_M=p1,p_D=p2)
  R_M_s_m[j,k] = Rs
  
  
  }
}

data_fix_delay <- expand.grid(diag_prob=p_D_seq,prob=p_seq)
data_fix_delay$R_M = c(R_M_m)
data_fix_delay$R_M_s = c(R_M_s_m)
```


```{r}
plot_p_D_p_M_R_M = ggplot(data_fix_delay, aes(y=diag_prob,x=prob,fill=R_M))+ 
geom_tile()+
labs(title="Heatmap of R_M when R0=3",  y="probability of diagnosis p_D", x="manual reporting probability p_M")+
# set contour breaks at desired level
geom_contour(aes(z = R_M), breaks = 2.25, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M), breaks = 2.75, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M), 
               breaks = 2, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M), 
               breaks = 2.5, col = 'black',size = 0.5,linetype ="dashed")+
  geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2.25,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2.75,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"),plot.subtitle = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu,sigma=sigma,beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_M")+
ylim(0.01, 1)

plot_p_D_p_M_R_M_s = ggplot(data_fix_delay, aes(y=diag_prob,x=prob,fill=R_M_s))+ 
geom_tile()+
labs(title="Heatmap of R_M when R0=1.5",  y="probability of diagnosis p_D", x="manual reporting probability p_M")+
# set contour breaks at desired level
geom_contour(aes(z = R_M_s), breaks = 1, col = 'black',size = 0.5)+
  geom_contour(aes(z = R_M_s), breaks = 1.4, col = 'black',size = 0.5,linetype ="dashed")+
  geom_contour(aes(z = R_M_s), breaks = 1.3, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M_s), breaks = 1.2, col = 'black',size = 0.5,linetype ="dashed")+
  geom_contour(aes(z = R_M_s), breaks = 1.1, col = 'black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
   geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
  geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
  geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.3,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
  geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.4,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"),plot.subtitle = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu,sigma=sigma,beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_M")+
ylim(0.01, 1)

# 2. Save the legend
#+++++++++++++++++++++++
legend = get_legend(plot_p_D_p_M_R_M)
# 3. Remove the legend 
#+++++++++++++++++++++++
plot_p_D_p_M_R_M <- plot_p_D_p_M_R_M + theme(legend.position="none")
plot_p_D_p_M_R_M_s <- plot_p_D_p_M_R_M_s + theme(legend.position="none")
# 4. Arrange ggplot2 graphs with a specific width
grid.arrange(plot_p_D_p_M_R_M, plot_p_D_p_M_R_M_s, legend, ncol=3, widths=c(2.3, 2.3,0.8))

```

# Heatmap of R_M (fix p_D, vary T_D and p_M)
```{r}
n_grid=100

# fix p_D = 0.8
p_D = 0.8

# p_M takes values in 
p_seq = seq(0,1, length.out=n_grid)

# T_D takes values in 
T_D_seq = seq(0,tau+T_L, length.out=n_grid)

# store the R_M values in a matrix:
R_M_m=matrix(nrow = n_grid,ncol = n_grid)

# store the R_M values in a matrix (for small R0)
R_M_s_m=matrix(nrow = n_grid,ncol = n_grid)


for (k in (1:n_grid)) {
  
  p = p_seq[k]
  
  for (j in (1:n_grid)) {
    
  t = T_D_seq[j] 
  
  R = R_manual_delay(mu=mu, sigma=sigma, beta_N= beta_N, beta_G= beta_G, 
                     tau=tau, T_L= T_L, p_D=p_D,
                     p_M=p,T_D=t)

  R_M_m[j,k] = R
  

  Rs = R_manual_delay(mu=mu, sigma=sigma, beta_N= beta_N_s, beta_G= beta_G_s, 
                     tau=tau, T_L= T_L, p_D=p_D,
                     p_M=p,T_D=t)

  
  R_M_s_m[j,k] = Rs
  
  
  }
}

data_fix_p_D <- expand.grid(delay=T_D_seq,prob=p_seq)
data_fix_p_D$R_M = c(R_M_m)
data_fix_p_D$R_M_s = c(R_M_s_m)

plot_T_D_p_M_R_M = ggplot(data_fix_p_D, aes(y=delay,x=prob,fill=R_M))+ 
geom_tile()+
labs(title="Heatmap of R_M when R0=3", 
   
  y="tracing delay", x="manual reporting probability p_M")+
# set contour breaks at desired level
geom_contour(aes(z = R_M), 
               breaks = 2.75, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M), 
               breaks = 2.5, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M), 
               breaks = 2.25, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M), 
               breaks = 2, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_M), 
               breaks = 1, col = 'black',size = 0.5)+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2.75,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2.25,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M), stroke = 0.1,breaks=2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"),plot.subtitle = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu, sigma=sigma, beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_M")+
ylim(0,7)

plot_T_D_p_M_R_M_s = ggplot(data_fix_p_D, aes(y=delay,x=prob,fill=R_M_s))+ 
geom_tile()+
labs(title="Heatmap of R_M when R0=1.5", 
    
  y="tracing delay", x="manual reporting probability p_M")+
# set contour breaks at desired level
geom_contour(aes(z = R_M_s), breaks = 1, col = 'black',size = 0.5)+
  geom_contour(aes(z = R_M_s), breaks = 1.1, col = 'black',size = 0.5,linetype ="dashed")+
  geom_contour(aes(z = R_M_s), breaks = 1.2, col = 'black',size = 0.5,linetype ="dashed")+
  geom_contour(aes(z = R_M_s), breaks = 1.3, col = 'black',size = 0.5,linetype ="dashed")+
  geom_contour(aes(z = R_M_s), breaks = 1.4, col = 'black',size = 0.5,linetype ="dashed")+
  geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
  geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
  geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.3,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
  geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1.4,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_M_s), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"),plot.subtitle = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu, sigma=sigma, beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_M")+
ylim(0,7)

# 2. Save the legend
#+++++++++++++++++++++++
legend = get_legend(plot_T_D_p_M_R_M)
# 3. Remove the legend 
#+++++++++++++++++++++++
plot_T_D_p_M_R_M <- plot_T_D_p_M_R_M + theme(legend.position="none")
plot_T_D_p_M_R_M_s <- plot_T_D_p_M_R_M_s + theme(legend.position="none")

# 4. Arrange ggplot2 graphs with a specific width
grid.arrange(plot_T_D_p_M_R_M, plot_T_D_p_M_R_M_s, legend,ncol=3, widths=c(2.3, 2.3,0.8))
```

# save the four heatmaps (R0=3,1.5, 50% transmission)
```{r}
grid.arrange(plot_p_D_p_M_R_M,plot_p_D_p_M_R_M_s, legend,plot_T_D_p_M_R_M, plot_T_D_p_M_R_M_s,ncol=3, widths=c(2.3, 2.3,0.8))
```

# Heat map of R_D for each combination of pi and p_D
```{r}
n_grid = 100

# pi takes values in 
pi_seq = seq(0,1, length.out=n_grid)

# p_D takes values in 
p_D_seq = seq(0.01,1, length.out=n_grid)

# store the R_D values in a matrix:
R_D_m=matrix(nrow = n_grid,ncol = n_grid)
# store the R_D values in a matrix (small R0)
R_D_s_m=matrix(nrow = n_grid,ncol = n_grid)

for (k in (1:n_grid)) {
  
  p1 = pi_seq[k]
  
  for (j in (1:n_grid)) {
    
  p2 = p_D_seq[j] 
  
  R = R_digital_network(mu=mu, sigma=sigma, beta_N= beta_N, beta_G= beta_G, 
             tau=tau, p_D=p2, T_L= T_L,
             pi=p1)
  
  Rs = R_digital_network(mu=mu, sigma=sigma,  beta_N= beta_N_s, beta_G= beta_G_s, 
             tau=tau, p_D=p2, T_L= T_L,
             pi=p1)
  
  R_D_m[j,k] = R
  R_D_s_m[j,k] = Rs
  
  }
}

# store all in a data frame 
data_dct <- expand.grid(diag_prob=p_D_seq,prob=pi_seq)
data_dct$R_D = c(R_D_m)
data_dct$R_D_s = c(R_D_s_m)
```

# Heatmap for R_D (vary with p_D and pi)

```{r}
plot_R_D = ggplot(data_dct, aes(y=diag_prob,x=prob,fill=R_D))+ 
geom_tile()+
labs(title="Heatmap of R_D when R0 = 3", y="probability of diagnosis p_D", x="app-using fraction pi_A")+
# set contour breaks at desired level
geom_contour(aes(z = R_D), breaks = 1, col ='black',size = 0.5)+
geom_contour(aes(z = R_D), 
               breaks = 1.5, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_D), 
               breaks = 2, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_D), 
               breaks = 2.5, col = 'black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_D), stroke = 0.1,breaks=2.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_D), stroke = 0.1,breaks=2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
  geom_text_contour(aes(z = R_D), stroke = 0.1,breaks=1.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
  geom_text_contour(aes(z = R_D), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu, sigma=sigma, beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_D")+
ylim(0.01, 1)


# heatmap for Reproduction Number for digital tracing (smaller R0)
plot_R_D_s = ggplot(data_dct, aes(y=diag_prob,x=prob,fill=R_D_s))+ 
geom_tile()+
labs(title="Heatmap of R_D when R0 = 1.5", y="probability of diagnosis p_D", x="app-using fraction pi_A")+
# set contour breaks at desired level
geom_contour(aes(z = R_D_s), breaks = 1, col ='black',size = 0.5)+
geom_text_contour(aes(z = R_D_s), stroke = 0.1,breaks=1,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_D_s), breaks = 1.4, col ='black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_D_s), breaks = 1.4, stroke = 0.1,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_D_s), breaks = 1.3, col ='black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_D_s), breaks = 1.3, stroke = 0.1,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_D_s), breaks = 1.2, col ='black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_D_s), breaks = 1.2, stroke = 0.1,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_D_s), breaks = 1.1, col ='black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_D_s), breaks = 1.1, stroke = 0.1,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu, sigma=sigma, beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_D")+
ylim(0.01, 1)

# 2. Save the legend
#+++++++++++++++++++++++
legend = get_legend(plot_R_D)
# 3. Remove the legend 
#+++++++++++++++++++++++
plot_R_D <- plot_R_D + theme(legend.position="none")
plot_R_D_s <- plot_R_D_s + theme(legend.position="none")

# 4. Arrange ggplot2 graphs with a specific width
grid.arrange(plot_R_D, plot_R_D_s,legend,ncol=3, widths=c(2.3, 2.3,0.8))
```

# Heat map of R_DM for each combination of p and pi
```{r}
# Fix p_D
p_D = 0.8
T_D = 3
# start compute R_DM for each combination of p and pi

n_grid = 100

# pi takes values in 
p_app_seq = seq(0,1, length.out=n_grid)
#p_app_seq # increment size with 0.99/99=0.01

# p takes values in 
p_manual_seq = seq(0,1, length.out=n_grid)

# store the R_DM values in a matrix:
R_DM_m=matrix(nrow = n_grid,ncol = n_grid)
R_DM_s_m=matrix(nrow = n_grid,ncol = n_grid)

for (k in (1:n_grid)) {
  
  p_A = p_app_seq[k]
  
  for (j in (1:n_grid)) {
    
  p = p_manual_seq[j] 
  
  R = R_comb(mu=mu, sigma=sigma, beta_N= beta_N, beta_G= beta_G, 
             tau=tau, p_D=p_D, T_L= T_L, T_D=T_D,
             p=p,pi=p_A)
  
  R_DM_m[j,k] = R
  
  Rs = R_comb(mu=mu, sigma=sigma, beta_N= beta_N_s, beta_G= beta_G_s, 
             tau=tau, p_D=p_D, T_L= T_L, T_D=T_D,
             p=p,pi=p_A)
  
  R_DM_s_m[j,k] = Rs
  
  
  }
}

# store in a data frame 

data_comb <- expand.grid(manual_prob=p_manual_seq,app_prob=p_app_seq)
data_comb$R_MD = c(R_DM_m)
data_comb$R_MD_s = c(R_DM_s_m)

# heatmap for the combined Reproduction Number for Manual and digital tracing

plot_R_MD = ggplot(data_comb, aes(y=app_prob,x=manual_prob,fill=R_MD))+ 
geom_tile()+
labs(title="Heatmap of R_MD when R0 =3", y="pi_A", x="p_M")+
# set contour breaks at desired level R_DM =1
geom_contour(aes(z = R_MD), 
               breaks = 1, col = 'black',size = 0.5)+
geom_contour(aes(z = R_MD), 
               breaks = 1.5, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_MD), 
               breaks = 2, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_MD), 
               breaks = 2.5, col = 'black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_MD), stroke = 0.1,breaks=2.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_MD), stroke = 0.1,breaks=2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_MD), stroke = 0.1,breaks=1.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_MD), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu,sigma=sigma,beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_MD")

plot_R_MD_s = ggplot(data_comb, aes(y=app_prob,x=manual_prob,fill=R_MD_s))+ 
geom_tile()+
labs(title="Heatmap of R_MD when R0 =1.5", y="pi_A", x="p_M")+
# set contour breaks at desired level R_DM =1
geom_contour(aes(z = R_MD_s), breaks = 1, col = 'black',size = 0.5)+
geom_text_contour(aes(z = R_MD_s), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_MD_s), breaks = 1.1, col = 'black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_MD_s), stroke = 0.1,breaks=1.1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_MD_s), breaks = 1.2, col = 'black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_MD_s), stroke = 0.1,breaks=1.2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_MD_s), breaks = 1.3, col = 'black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_MD_s), stroke = 0.1,breaks=1.3,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_contour(aes(z = R_MD_s), breaks = 1.4, col = 'black',size = 0.5,linetype ="dashed")+
geom_text_contour(aes(z = R_MD_s), stroke = 0.1,breaks=1.4,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(text = element_text(size=10))+
theme(plot.title = element_text(hjust = 0.5,face = "bold"))+
scale_fill_distiller(palette = "RdYlBu",limits = c(0,R_0(mu=mu,sigma=sigma,beta_N = beta_N, beta_G = beta_G, tau=tau)),"R_MD")


# 2. Save the legend
#+++++++++++++++++++++++
legend = get_legend(plot_R_MD)
# 3. Remove the legend 
#+++++++++++++++++++++++
plot_R_MD <- plot_R_MD + theme(legend.position="none")
plot_R_MD_s <- plot_R_MD_s + theme(legend.position="none")

# 4. Arrange ggplot2 graphs with a specific width
grid.arrange(plot_R_MD, plot_R_MD_s,legend,ncol=3, widths=c(2.3, 2.3,0.8))

```

# plot the reproduction numbers against the variance of D

```{r}
# the sequences of reproduction number of MCT, DCT, combined CT and R_0
R_0_seq = c()
R_M_seq = c()
R_D_seq = c()
R_MD_seq = c()

n_grid = 101
sigma_2_seq = seq(0,100, length.out=n_grid)

# infectious period (deterministic)
tau=5
# latency period (deterministic)
T_L=4
# mean degree 
mu = 5
# fix 
p_D = 0.8 
T_D = 3

# we choose beta_G beta_N so that R0 =3 in the case of sigma=0

f_beta <- function(x){R_0(mu=mu, sigma=0, 
                    beta_G = mu*x, beta_N = x, 
                    tau=tau)-3}

beta_N = uniroot(f_beta,c(0,1))$root
beta_G = mu*beta_N


#R_0_start = R_0(mu=mu, sigma=0, beta_N= beta_N, beta_G= beta_G, tau=tau)

# fix the p_M
pM_fix = 0.5

R_M_start = R_manual_delay(mu=mu,sigma = 0,
                          beta_N= beta_N, beta_G= beta_G, 
                          tau=tau,T_L= T_L,T_D = T_D,
                          p_D=0.8, p_M=pM_fix)

# Choose pi_A so that R_D starts with the same value of R_M 
f1 <- function(x){R_digital_network(mu=mu,sigma = 0, 
                             beta_N= beta_N, beta_G= beta_G, 
                             tau=tau,T_L= T_L,
                             p_D=0.8, pi=x)-R_M_start}

pi_fix = uniroot(f1,c(0,1))$root


for (j in (1:n_grid)) {
    
    s = sigma_2_seq[j]

    R = R_0(mu=mu, sigma=sqrt(s), 
            beta_N= beta_N, beta_G= beta_G, 
            tau=tau)

    
    R_dct= R_digital_network(mu=mu,sigma = sqrt(s), 
                             beta_N= beta_N, beta_G= beta_G, 
                             tau=tau,T_L= T_L,
                             p_D=0.8, pi=pi_fix)
    
    R_mct= R_manual_delay(mu=mu,sigma = sqrt(s),
                          beta_N= beta_N, beta_G= beta_G, 
                          tau=tau,T_L= T_L,T_D = T_D,
                          p_D=0.8, p_M=pM_fix)
    
    R_md = R_comb(mu=mu,sigma = sqrt(s),beta_N= beta_N, beta_G= beta_G, 
                  tau=tau,T_L= T_L, T_D = T_D,
                  p_D=0.8, pi=pi_fix, p_M=pM_fix)
    
    R_0_seq = c(R_0_seq, R)
    R_M_seq = c(R_M_seq, R_mct)
    R_D_seq = c(R_D_seq, R_dct)
    R_MD_seq = c(R_MD_seq, R_md)
  
}


df <- data.frame(
    Var_D = c(sigma_2_seq,sigma_2_seq,sigma_2_seq,sigma_2_seq),
    r = c(R_0_seq,R_M_seq,R_D_seq,R_MD_seq),
    R = c(rep("R_0", n_grid), rep("R_M", n_grid),rep("R_D", n_grid),rep("R_MD", n_grid)))

ggplot(df, aes(x = Var_D, y = r, group = R, col = R,linetype = R))+ 
geom_line()+
ylab("reproduction number")+
xlab("Variance of D")+
scale_color_manual(values = c("R_0" = "red",
                              "R_M"="#ff9200", 
                                 "R_D"="#0094ff",
                                  "R_MD" = "#54B345"))+
scale_linetype_manual( values = c("R_0"="solid", 
                                    "R_M"="solid",
                                    "R_D" = "solid",
                                  "R_MD" = "solid"))+
xlim(0,100)
```

# plot the corresponding reduction factors against the variance of D


```{r}
r_M_seq = (R_0_seq-R_M_seq)/R_0_seq
r_D_seq = (R_0_seq-R_D_seq)/R_0_seq
r_MD_seq = (R_0_seq-R_MD_seq)/R_0_seq

df_r <- data.frame(
    Var_D = c(sigma_2_seq,sigma_2_seq,sigma_2_seq),
    r = c(r_M_seq,r_D_seq,r_MD_seq),
    reduction = c(rep("r_M", n_grid), rep("r_D", n_grid),rep("r_MD", n_grid)))

ggplot(df_r, aes(x = Var_D, y = r, group = reduction, col = reduction,linetype = reduction))+ 
geom_line()+
ylab("r_M, r_D, r_MD")+
xlab("Variance of D")+
scale_color_manual(values = c("r_M"="#ff9200", 
                                 "r_D"="#0094ff",
                                  "r_MD" = "#54B345"))+
scale_linetype_manual( values = c("r_M"="solid", 
                                    "r_D"="solid",
                                    "r_MD" = "solid"))+
ylim(0,0.5)+
xlim(0,100)
```

